The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-28 paper.tex
added back the mirror neurons in 2.2.2 and phase 1 and 2 of cog model

%\paragraph{Mirror neurons and resonnance behaviors \\}
%
%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.  
%
%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
%
%Interestingly, there are good evidence showing that motor mirror neurons in the
%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms. %mirror neurons
%
%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
%
%The response of the human brain to a social signal perceived on a robot, such as facial
%emotional expression is less evident. 
%
%In studying emotional perception in a human or a robot face using functional
%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
%in response to the robot stimuli than to the human stimuli in emotional brain
%areas known to have mirror properties. However if the subject was asked to
%specifically attend to the emotional content of the stimuli, processing of the
%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
%
%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
%
%
%
%

In sum, this branch of research suggests that anthropomorphism implies that
people thoughtfully develop a mental model of agents in their environment and
that they make inferences about these agents based on what is familiar to them
-- themselves, humans and human behavior. This understanding builds on the
theory of mind,  a
person's ability to attribute mental states to oneself and others. 
%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
We briefly reviewed  neuro-physiological evidence of a link between the tendency
to thoughtfully anthropomorphize and the engagement of brain processes involved
in the attribution of mental states to other humans. The human-likeness quality
of the artefactual agent seems to play a role in the involvement of theory of
mind but also the unpredictable feature of the agent behavior alone seems to be
sufficient.  
%were recently demonstrated at the brain level~\citep{cullen2013individual}.

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.

@@

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}). 
%At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.

>>>>

At lower, more automatic, level, robots have been shown to elicit resonnance behaviors in the
human brain. Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.  
The neurons showing resonnant properties have been called mirror neurons and
have been found in a wide range of modalities (motor, emotional etc..)
\fixme{addref}.Seeing a robotic arm reaching for an object activates the motor mirror neurons the same way as for seeing a human arm reaching for the same object
\citep{Gazzola2007, oberman_eeg_2007}. However, a study of emotion perception
on a robotic face found reduced activity in emotional brain
area known to have mirror properties in response to the robotic face compared to
a human face \citep{Chaminade2010}. Nevertheless, these authors showed that when
the participants were explicitely instructed to pay attention to the robot's
emotional expression, motor mirror neurons gets activated.
Interestingly, using electroencephalography,  it has also been shown that
emotional behavior elicited by a robot face influences the speed of human
responses as well as early brain processes the same way as emotional expression
of a human face did \citep{Dubal2010}.

In sum, this branch of research suggests that anthropomorphism implies that
people thoughtfully develop a mental model of agents in their environment and
that they make inferences about these agents based on what is familiar to them
-- themselves, humans and human behavior. This understanding builds on the
theory of mind,  a
person's ability to attribute mental states to oneself and others. 
%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
We briefly reviewed  neuro-physiological evidence of a link between the tendency
to thoughtfully anthropomorphize and the engagement of brain processes involved
in the attribution of mental states to other humans. The human-likeness quality
of the artefactual agent seems to play a role in the involvement of theory of
mind but also the unpredictable feature of the agent behavior alone seems to be
sufficient. Low-level mechanisms of the brain that allow humans to map other's
motor behaviors into their own repertoire are equally elicited when perceiving a
robot's action. It is not yet clear whether human are processing emotional
signal from a robot the same way as they do for human beings. 
%were recently demonstrated at the brain level~\citep{cullen2013individual}.

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
It is also at this stage that automatic activation of the human's mirror neurons
system  in response to viewing the robots action and human automatic emotional
responses are contributing at a lower level
to the intuitive anthropomorphization (see Section 2.2.2 \fixme{put ref})
%We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.

@@

After a longer observation period (typically including complete action sequences
of the robot) or short interaction (touching, short talk like greetings), we
suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
starts building a behavioral and cognitive model of the robot that would support
both the observed and imagined capabilities of the robot.  The \emph{familiarity
thesis}~\cite{hegel_understanding_2008} supports the idea that the human
first projects onto the robot mental models of similar agents he/she is already
familiar with (ranging from animals to human adults, to pets and children). We 
hypothesize that the nature of the projected mental
model, as well as how deep the human engages in this projection, might be
driven by the same parameters as we mentioned for the \emph{initial capital of
anthropomorphism} (section~\ref{sec:ica}). 
At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
